Online Verification of Commutativity

### 2020-09-10 acmPaper/paper.tex
Minor changes

We then create a set $P$ of all the paths in the diagram with no cycles, and filter the set $P \times P$, excluding pairs where the paths begin or end on different nodes, or are identical, to get the set of all cycle-free parallel pairs $Q$.
After verifying $C$, it is sufficient to verify only $Q$ (as opposed to all pairs, per Lemma~\ref{one_occurence_lemma}) because cycles must now be the identity, so for any pair in the set of all parallel paths, any instance of a cycle can be removed to obtain an equivalent pair with shorter, cycle-free paths.

@@

This narrowing can be done because the original diagram commutes.
Pairs where both paths do not involve the new edge would remain equal (this would apply to cycles too; cycles that do not pass through the new edge must be the identity).
Also, pairs where both paths involved the new edge would have to be equal.
To see why this is true, each path could be thought of as consisting of the composition of three segments.
For path pair $p$, and new edge from node $S$ to node $T$, the first segment extends from $\partial(p)^+$ to the $S$, the second, the new edge $(S, T)$ itself, and the third, from $T$ to $\partial(p)^-$.
The new edge could only appear once because cycles have already been dealt with so only pairs where the path includes the new edge once need be checked (Lemma~\ref{one_occurence_lemma}).
The first segment of both pairs would have to be equal because they existed as parallel pairs in the original diagram, and similarly the third segments would also have to be equal.
The second segments, consisting of the same edge, would also have to be equal because the equivalence oracle is reflexive.
Therefore, the two paths of the pair, a composition of these three equal components, would be equal, since the oracle would preserve transitivity of equality.
We are left only with parallel pairs where exactly one of the paths passes through the new edge.

@@

\begin{lemma}
\label{one_occurence_lemma}
A path that involves the new edge more than once is equal to a path without multiple occurrences of the edge, under the assumption that the pairs in C are verified.
\end{lemma}
\begin{proof}
Consider the part of the path between the first occurrence of the new edge and the second. This forms a cycle, which has a corresponding check in $C$ and must be verified to be equal to the identity.
This means that the loops containing the multiple occurrences of the new edge may be ignored and the path with a single occurrence of the new edge with the cycles removed is equal to this path.
\end{proof}

>>>>

We then create a set $P$ of all the paths in the diagram with no cycles, and filter the set $P \times P$, excluding pairs where the paths begin or end on different nodes, or are identical, to get the set of all cycle-free parallel pairs $Q$.
After verifying $C$, it is sufficient to verify only $Q$ (as opposed to all pairs) because cycles must now be the identity, so for any pair in the set of all parallel paths, any instance of a cycle can be removed to obtain an equivalent pair with shorter, cycle-free paths.

@@

This narrowing can be done because the original diagram commutes.
Pairs where both paths do not involve the new edge would remain equal (this would apply to cycles too; cycles that do not pass through the new edge must be the identity).
Also, pairs where both paths involved the new edge would have to be equal.
To see why this is true, each path could be thought of as consisting of the composition of three segments.
For path pair $p$, and new edge from node $S$ to node $T$, the first segment extends from $\partial(p)^+$ to the $S$, the second, the new edge $(S, T)$ itself, and the third, from $T$ to $\partial(p)^-$.
The new edge could only appear once because cycles have already been dealt with so only pairs where the path includes the new edge once need be checked.
The first segment of both pairs would have to be equal because they existed as parallel pairs in the original diagram, and similarly the third segments would also have to be equal.
The second segments, consisting of the same edge, would also have to be equal because the equivalence oracle is reflexive.
Therefore, the two paths of the pair, a composition of these three equal components, would be equal, since the oracle would preserve transitivity of equality.
We are left only with parallel pairs where exactly one of the paths passes through the new edge.

@@
